From Freebase to Wikidata: The Great Migration

### 2015-10-15 paper.tex
added section related work (still empty)

The remainder of this paper is structured as follows.
After an introduction to the two collaborative knowledge bases
Freebase and Wikidata in \autoref{sec:background},
we describe our methodology and the metrics used to measure the migration
in \autoref{sec:challenges-of-the-migration}.
In order to support the migration, we have developed a~set of open source tools
that we present in \autoref{sec:primary-sources-tool}.
We then present the results of the migration
and discuss these statistics in \autoref{sec:statistics-of-the-migration}.
The paper terminates with an outlook at proposed next steps
and a~conclusion in \autoref{sec:future-work-and-conclusion}.

@@

Freebase is an open source and
collaborative knowledge base created in 2007 by Metaweb and acquired in 2010 by Google.
It was used as the open core of the Google Knowledge Graph,
and also has many use cases outside of Google.

Due to the success of Wikidata,
it was decided to close Freebase and support the migration of its content to Wikidata.
Freebase relies on the notions of \emph{topics}, \emph{facts}, \emph{types}, and \emph{properties}.
Each Freebase topic has a~stable identifier called \emph{``mid''} (for Metaweb ID),
one or more types, and uses properties from these types in order to provide facts.
For example, the Freebase topic for Barack Obama has the mid \texttt{/m/02mjmr}
and the type \texttt{/government/us\_president} that allows the entity to have
a fact with the property \texttt{/government/us\_president/presidency\_number}
and the literal integer ``44'' as the value.

@@

>>>>

The remainder of this paper is structured as follows.
After an introduction to the two collaborative knowledge bases
Freebase and Wikidata in \autoref{sec:background},
we describe our methodology and the metrics used to measure the migration
in \autoref{sec:challenges-of-the-migration}.
In order to support the migration, we have developed a~set of open source tools
that we present in \autoref{sec:primary-sources-tool}.
We then present the results of the migration
and discuss these statistics in \autoref{sec:statistics-of-the-migration}.
In \autoref{sec:related-work} we discuss the relation to other work.
The paper terminates with an outlook at proposed next steps
and a~conclusion in \autoref{sec:future-work-and-conclusion}.

@@

Freebase is an open source and
collaborative knowledge base created in 2007 by Metaweb and 
acquired in 2010 by Google~\cite{freebase}.
It was used as the open core of the Google Knowledge Graph,
and also has many use cases outside of Google.

Due to the success of Wikidata,
it was decided to close Freebase and support the migration of its content to Wikidata.
Freebase relies on the notions of \emph{topics}, \emph{facts}, \emph{types}, and \emph{properties}.
Each Freebase topic has a~stable identifier called \emph{``mid''} (for Metaweb ID),
one or more types, and uses properties from these types in order to provide facts.
For example, the Freebase topic for Barack Obama has the mid \texttt{/m/02mjmr}
and the type \texttt{/government/us\_president} (among others) that allows the entity to have
a fact with the property \texttt{/government/us\_president/presidency\_number}
and the literal integer ``44'' as the value.

@@

\section{Related Work}\label{sec:related-work}

There has been a lot of research on ontology mapping.
